\documentclass[times, 10pt,twocolumn]{article} 
\usepackage{latex8}    
\usepackage{times}
\usepackage{url}  
\usepackage{listings}
\newcounter{firstbib} 
 
\pagestyle{empty}

\begin{document}  

\title{Large Scale and High Performance NoSQL Databases in Web Applications} 
\author{Mateusz Bilski, mateusz.bilski@gmail.com \\ Ireneusz Kawalec, ireneusz.kawalec@gmail.com \\ \\
Wroclaw University of Technology\\ Faculty of Electronics \\ Computer Science \\ Internet Engineering  \\  
} 

\maketitle
\thispagestyle{empty} 

\begin{abstract}   

In our project we are going to present comparison between available NoSQL
databases and architecture which provides high performance for large scale web applications.

The article describes methods which are used for building large scale database
systems and also contains valuable information regarding optimization operations
on lots of data.

The final outcome of this paper is comparison of 5 most common NoSQL
databases based on mean response time (read, write operations).

\end{abstract} 

keywords: database, NoSQL, large scale, high performance, web application 

%-------------------------------------------------------------------------

\Section{Background}

A database is an organized collection of data. It is designed to offer an organized mechanism for storing, 
managing and retrieving information.

Databases can be classified due to their organizational approach. Two main
types of database can be distingeshed: relational database, no-relational
database.

In Relational Database information is represented as a collection of tables. 
Each table consist of columns and rows. The columns contains only simple
type, i.e: Number, Date, Char. One column in table called Primary Key
is used to differ row. Primary key must be a unique. If we want to connect 
two tables, foreign key are used.

In no-relation database information is represented as an object.
The basic approach is key-value stores. To obain a value, the key must be
provided (in these case key and value are simple types). More
advanced solutions insted of returning simple type as a value, returns 
the object. The object has no stricted schema.

Databases are used to build information systems. Large systems contains a lots of data and manipulate with them
every seconds. Such systems must provide high performance (being able to handle thousand of reading and writing operations
per second) and high availability (often over 99.9999\% of uptime in a year). Furthermore systems consist of many servers, so 
they should be horizotaly scalable - has a ability to add more nodes to a system, such as adding a new computer to a distributed 
application. This allows to increase performance and availability.

\Section{Introduction}

Databases are used almost in all aspects of software engineering. Each 
system needs a place to storage a data. 

Modern web applications should be able to handle a huge load and provide high performance. 
Good examples of such services are Facebook, Amazon, eBay and Google Mail. Most of them use NoSQL databases
instead of SQL to achieve better performance.

A NoSQL database provides a mechanism for storage and retrieval of data that use looser consistency models 
than traditional relational databases in order to achieve horizontal scaling and higher availability. Some authors 
refer to them as "Not only SQL" to emphasize that some NoSQL systems do allow SQL-like query language to be used.

The architecture of database system has a big influence of performance. Single machine has a limited
resources, so this is a reason why enterprise systems are composed of a lot of them.

We have done a Systematic Literature Review for this topic. There are some studies describing high performance 
and scalable NoSQL databases, but there is really no specific document which would describe real world scenario like 
database (type, configuration) for web application able to handle millions of users. This is a gap we want to fulfill.

%------------------------------------------------------------------------- 
\Section{Aims and Objectives}

Aim
\begin{itemize}
	\item to evaluate performance of NoSQL databases for large scale web applications.
\end{itemize}

\vspace{1cm}

Objectives
\begin{itemize}
	\item to design architecture of system for high performance and large scale web application using NoSQL databases
	\item to develop an optimal configuration for prepared architecture for each database
	\item to measure reading and writing response time of the system for each database
\end{itemize} 


\Section{Expected Outcomes}

The expected outcomes of the research are:

\begin{itemize}
  \item architecture and configuration of NoSQL databases which provides high performance on large scale database systems
  \item tests results of measuring reading/writing response time of each NoSQL databases on prepared architecture and configuration.
\end{itemize}

\Section{Research Questions}

In our paper we want to give answers to the following questions:

\begin{enumerate}
  \item What is the best architecture for large scale, high performance NoSQL databases?
  \item How to configure NoSQL databases to gain maximum efficiency?
  \item What are reading and writing response times for top used NoSQL databases?
  \item Which NoSQL database is the best for large scale, high performance database systems?
\end{enumerate}
 
\Section{Methods}

For the first step of our research: design architecture and preparing configuration, we decided to use Action Research method.
We are going to choose most known databases using rankings available on the internet and then by investigating
documentation learn more about them and find out how to design and configure a system to be the most efficient.

To tests the databases we are going to conduct an experiment. We want to measure response time of the large scale
system for each database.

\Section{Project Plan}

\begin{enumerate}
  \item Choose the five most used NoSQL databases
	\begin{enumerate}
	  \item Find articles describing NoSQL databases
	  \item Choose five the most often used databases according to articles 
	\end{enumerate}
  \item Design an architecture of the system
	\begin{enumerate}
	  \item Find methods which are used for building large scale database systems
	  \item Find which methods ensure high performance
	  \item Use methods to design an architecture
	\end{enumerate}
  \item Find out the configuration for each database to be the most efficient on prepared architecture
    \begin{enumerate}
	  \item Find the optimization techniques for database dedicated systems
	  \item Find the database configuration to optimize operations on lots of data
	  \item For each database build system for designed architecture using prepared configuration
	\end{enumerate}
  \item Measure response times of each database
    \begin{enumerate}
      \item Prepare test suites
      \item Measure read and write time   
    \end{enumerate}  
\end{enumerate}

\Section{Results}

	\begin{enumerate}
	  \item Choose the five most used NoSQL databases
	\end{enumerate}
	
	We did Systematic Literature Review \cite{slr} to obtain 5 most common
	NoSQL databases. We explored available digital libraries such as ACM, IEEEXplore,
	Google Scholar and after couple of interations and rejections based on
	excludion criteria we received following list of NoSQL databases: MongoDB, Cassandra, CouchDB, Redis and Voldemort.  

\section{Threats to validity}

\begin{itemize}
	\item choosed databases are the most used. There may exists better but not popular database.
	\item to design architecture and prepare configuration we used documentation and articles. Results might be better if database experts would be involved
	\item machines used by us to perform load testing (bought in amazon cloud) might be distributed between many local networks. That would 
	couse decrease of performance and the results might be better in optimized environment
\end{itemize}

\begin{thebibliography}{9}  

\setcounter{enumiv}{\value{firstbib}}
      
      \bibitem{research_methods} 
      Ludwik Kuzniarz
      \emph{Lecture 5: Writing Project Proposal, Research Methodology course at WUT}. Blekinge Institute of Technology
      
      \bibitem{slr} 
      Mateusz Bilski, Ireneusz Kawalec
      \emph{Systematic Literature Review of Large Scale and High Performance NoSQL Databases in Web Applications}. Wroclaw University of Technology
      
      \bibitem{nosql-database}
      \emph{List of NoSQL Databases} \\
      \url{http://nosql-database.org/}

\end{thebibliography}

\end{document}
